---
title:  "Test fixtures: Reusing test data configuration between tests"
author: "Bai Li <br> <br> National Stock Assessment Modeling Team <br> Contractor with ECS in support of NOAA Fisheries <br> Office of Science and Technology <br> `bai.li@noaa.gov`"
date: "Nov 17, 2022 <br> FIMS C++ office hour <br> Updated on `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css"]
    lib_dir: libs
    nature:
      ratio: '4:3'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "Page %current%"
---
layout: true
  

```{r xaringanthemer, include=FALSE, warning=FALSE}
required_pkg <- c("DiagrammeR", "xaringanthemer", "remotes")
pkg_to_install <- required_pkg[!(required_pkg %in%
                                   installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)
lapply(required_pkg, library, character.only = TRUE)

remotes::install_github("nmfs-general-modeling-tools/nmfspalette")
library(nmfspalette)



static_dir <- file.path("static")
noaa_static_dir <- file.path(static_dir, "noaa_static")
general_dir <- file.path(static_dir, "general")

# make colors css names

style_xaringan(
  
  base_font_size = "15px",
  text_font_size = "1.5rem",
  
  title_slide_background_color = unname(nmfs_cols("darkblue")),
  title_slide_text_color = unname(nmfs_cols("white")),
  title_slide_background_size = "cover",
  title_slide_background_image = file.path(noaa_static_dir, "slideswooshver.png"),
  
  background_image = file.path(noaa_static_dir, "slideswoosh.PNG"),
  background_size = "cover",
  background_color = unname(nmfs_cols("white")),
  
  header_font_google = google_font("Arimo"),
  header_color = unname(nmfs_cols("darkblue")),
  
  text_color = unname(nmfs_cols("darkblue")),
  text_font_google = google_font("Carlito", "300", "300i"),
  text_slide_number_color = unname(nmfs_cols("lightteal")),
  
  code_font_google = google_font("Source Code Pro"),
  code_highlight_color = unname(nmfs_cols("medteal")),
  
  inverse_background_color = unname(nmfs_cols("processblue")),
  inverse_text_color = unname(nmfs_cols("supltgray")),
  
  footnote_font_size = "0.6em",
  footnote_color = unname(nmfs_cols("darkblue")),
  footnote_position_bottom = "10px",
  
  link_color = unname(nmfs_cols("medteal")),
  
  
  extra_css = list(
    ".remark-slide-number" = list(
      "font-size" = "0.4em",
      "font-weight" = "bold",
      "margin" = "0px 840px -2px 0px"),
    
    ".title-slide h1, h2, h3" = list(
      "text-align" = "right")
  )
)
```

.footnote[U.S. Department of Commerce | National Oceanic and Atmospheric Administration | National Marine Fisheries Service]


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

```

---
# Test fixture definition

- An object the test runs against*<sup>1</sup>*
  - can be a regular dependency: an argument to be passed, data in the database, or a file on the hard disk
  - remain in a known and fixed state to produce the same results before executing tests
  
- Help set up **custom initialization work** for multiple tests*<sup>2</sup>*
  - preconditions 
  - data
  - cleanup procedures
  
.center[**Use test fixture when you find you are repeating yourself**]

.footnote[
[1]Khorikov V. 2020. Unit testing: principles, practices, and patterns. Shelter Island, NY: Manning.<br>
[2]GoogleTest Users' guide: [http://google.github.io/googletest/primer.html#same-data-multiple-tests](http://google.github.io/googletest/primer.html#same-data-multiple-tests) <br>
]

---
**CalculateMortality_works and CalculateNumbersAA_works share same initialization work**

```c++
TEST(PopulationModuleTest, CalculateMortality_works)
{
  fims::Population<double> population;
  population.nyears = 30;
  population.nages = 12;
  int year = 2;
  int age = 7; 
  int index_ya = year * population.nages + age;
  
  population.CalculateMortality(index_ya, year, age);
  
  EXPECT_EQ(population.mortality_F[index_ya], 3.5);
}
```

```c++
TEST(PopulationModuleTest, CalculateNumbersAA_works)
{
  fims::Population<double> population;
  population.nyears = 30;
  population.nages = 12;
  int year = 4;
  int age = 6; 
  int index_ya = year * population.nages + age;
  int index_ya2 = (year - 1) * population.nages + age - 1;
  
  population.CalculateNumbersAA(index_ya, index_ya2);
  
  EXPECT_EQ(population.numbers_at_age[index_ya], 1234);      
}
```
---
# Google Test template
.pull-left[
- Simple test

```c++
Test(TestSuiteName, TestName1){
  ...test body...
}

Test(TestSuiteName, TestName2){
  ...test body...
}
```
]

.pull-right[
- Fixture test

```c++
Test_F(TestFixtureName, TestName1){
  ...test body...
}

Test_F(TestFixtureName, TestName2){
  ...test body...
}
```
]
---
# Steps to create a Google Test fixture class*<sup>1</sup>*
- Derive a class from `::testing::Test`
- Start its body with `protected:` to access fixture members from sub-classes
- Declare any objects you plan to use inside the class
- Write a default constructor or `SetUp()` function to prepare the objects
- Write a destructor or `TearDown()` function to release any resources that are allocated in `SetUp`. 
- Define subroutines for your tests to share
  
```c++
class TestFixtureName : public ::testing::Test{
  protected:
    void SetUp override{
      ...SetUp body...
    }
    
    void TearDown() override {
    ...TearDown body...
    }
    
    ...Other subroutines...
}
```
.footnote[
[1]GoogleTest Users' guide: [http://google.github.io/googletest/primer.html#same-data-multiple-tests](http://google.github.io/googletest/primer.html#same-data-multiple-tests) <br>
]
---
# FIMS test fixture files (WIP)
- FIMS/tests/gtest/test_population_test_fixture.hpp ([link](https://github.com/NOAA-FIMS/FIMS/blob/633a707101b0638f0fe7374d055636e41a57126c/tests/gtest/test_population_test_fixture.hpp))
- FIMS/tests/gtest/test_population_dynamics_population_initialize_prepare.cpp([link](https://github.com/NOAA-FIMS/FIMS/blob/633a707101b0638f0fe7374d055636e41a57126c/tests/gtest/test_population_dynamics_population_initialize_prepare.cpp))
- FIMS/tests/gtest/test_population_NumbersAtAge.cpp([link](https://github.com/NOAA-FIMS/FIMS/blob/633a707101b0638f0fe7374d055636e41a57126c/tests/gtest/test_population_NumbersAtAge.cpp))
- FIMS/tests/gtest/test_population_Li.cpp ([link](https://github.com/NOAA-FIMS/FIMS/blob/633a707101b0638f0fe7374d055636e41a57126c/tests/gtest/test_population_Li.cpp))
---
# FIMS test files diagram
```{r echo=FALSE, out.width="100%"}
DiagrammeR::mermaid("
graph LR
  1[<center><b>test_population_test_fixture.hpp</b></center>];
  2[PopulationInitializeTestFixture];
  3[PopulationPrepareTestFixture];
  2-1[<center><b>test_population_dynamics_population_initialize_prepare.cpp</b></center><br>test: input_data_are_specified];
  2-2[<center><b>test_population_dynamics_population_initialize_prepare.cpp</b></center><br>test: Initialize_works];
  3-1[<center><b>test_population_dynamics_population_initialize_prepare.cpp</b></center><br>test: Prepare_works];
  3-2[<center><b>test_population_NumbersAtAge.cpp</b></center><br>test: CalculateNumbersAA_works];
  3-3[<center><b>test_population_Li.cpp</b></center><br>test: CalculateMortality_works];
  1-->2
  1-->3
  2-->2-1
  2-->2-2
  3-->3-1
  3-->3-2
  3-->3-3
")
```
---
# PopulationInitializeTestFixture
- `PopulationInitializeTestFixture` derives from the fixture base class `::testing::Test`
- Population id_g, nyears, nseasons, nages, nfleets, and fleet from the SetUp() will be called **before** all tests using the fixture
- TearDown() will be called **after** all tests using the fixture are run
- Population object will be called and id_g, nyears, nseasons, nages, nfleets values will be set before calling SetUp()
---
# PopulationPrepareTestFixture
  - population.Initialize() and population.Prepare() functions will be called **before** all tests using the fixture
  - population.log_naa, population.log_M, population.log_Fmort pseudo-random numbers will be generated using `std::default_random_engine` class **before** all tests using the fixture
  - Make shared pointers to selectivity, fleet, and maturity to set up population.fleets and maturity
---
# Thanks!

bai.li@noaa.gov


